---
title_meta  : Chapter 1
title       : The grammar of graphics
description : In this chapter, you will learn about the grammar of graphics conceptual framework, and its different components. This chapter will require very little coding.
framework   : datacamp
mode        : selfcontained

---

## How it works

In the **editor** on the right you will have to type your code to solve the exercises.

Since understanding and structuring long parts of code is not always straight-forward, R makes use of the `#` sign to add comments. Just like Twitter! Comments are not run as R-code, so they will not influence your result. 

The output of your R code shows in the **console** in the lower right corner, while **graphs** are shown in the upper right corner.

*** =instructions

  - Click Submit Answer and see how the console now shows you the executed R code: the solution `7` appears as the sum of `3` and `4`. In its most basic form R can thus be used as a calculator or to generate plots, but there's much more ;-).
  - Use the arrows to browse through some cool visualizations generated by R upper right corner. Note that you can make the graph window larger if you would like to have a closer look.

*** =hint
Just click the Submit Answer button on the right.

*** =sample_code

```{r eval=FALSE}
# This  is the editor and the part below the white line is called the console

# The  hashtag is used to add comments

# Show some demo graphs generated with R
demo("graphics")

# Calculate 3+4
3+4
```

*** =solution

```{r eval=FALSE}
#Just click the Submit Answer button

# This  is the editor and the part below the white line is called the console

# The  hashtag is used to add comments

# Calculate 3+4
3+4

# Show some demo graphs generated with R
demo("graphics")
```

*** =sct

```{r eval=FALSE}
DM.result = list(TRUE, "Great! Let's get started!");
```

*** =pre_exercise_code

```{r eval=FALSE}

```

---
## Our dataset
In this chapter, we will work with a toy dataset that will allow us to easily inspect each components of the grammar of graphics. The name of the dataset is **mini_walmart**. It contains the number of Walmart stores in 5 US States in the year 2005. 

*** =instructions
  - The first thing we want to do is to take a look at the dataset we are going to work with.
  Print the `mini_walmart` dataset on the screen 

*** =hint

Add a hint

*** =pre_exercise_code

```{r,eval=FALSE}
# Pre-exercise code is executed before the exercise starts (what's in a name...)
# It can be used to:
# Pre-load a dataset
# Render graphs that are shown at the start of the exercise
# ...
year <- c(2005, 2005, 2005, 2005, 2005)
state <- c("FL", "MI", "NJ", "NV", "VT")
stores <- c(174, 76, 41, 22, 4) 
mini_walmart <- data.frame(year, state, stores)
```

*** =solution

```{r,eval=FALSE}
# The solution code solves the assignement. Make sure the solution passes the submission correctness test (we will check this;-)!
mini_walmart
```

*** =sample_code

```{r,eval=FALSE}
# The dataset has been pre-loaded. Just type mini_walmart and click submit to inspect the full data set
```

*** =sct

```{r,eval=FALSE}
# The Submission Correctness Test code
# It takes as input the students workspace, his code and what was printed to the console during the exercise.
# Based on these inputs the SCT returns:
# (i) whether the students code was correct
# (ii) a message to the student to either help him find what was wrong or congragulate him on finding the solution.
DM.result = list(TRUE,"Well done!")
```

---
## GG components: Aesthetics
To complete

*** =instructions
  - To complete

*** =hint

Add a hint

*** =pre_exercise_code

```{r,eval=FALSE}
# Pre-exercise code is executed before the exercise starts (what's in a name...)
# It can be used to:
# Pre-load a dataset
# Render graphs that are shown at the start of the exercise
# ...
library(ggplot2)
year <- c(2005, 2005, 2005, 2005, 2005)
state <- c("FL", "MI", "NJ", "NV", "VT")
stores <- c(174, 76, 41, 22, 4) 
mini_walmart <- data.frame(year, state, stores)

aes_position <- ggplot() + geom_point(aes(x = state,y = stores), size = 5, data = mini_walmart)
print(aes_position)
```

*** =solution

```{r,eval=FALSE}
# The solution code solves the assignement. Make sure the solution passes the submission correctness test (we will check this;-)!
print(aes_position)
```

*** =sample_code

```{r,eval=FALSE}
# Print chart
```

*** =sct

```{r,eval=FALSE}
# The Submission Correctness Test code
# It takes as input the students workspace, his code and what was printed to the console during the exercise.
# Based on these inputs the SCT returns:
# (i) whether the students code was correct
# (ii) a message to the student to either help him find what was wrong or congragulate him on finding the solution.
DM.result = list(TRUE,"Well done!")
```






## The title of the first exercise

1. Complete YAML front matter above
2. Write using R Markdown (http://en.wikipedia.org/wiki/Markdown)
3. Start an exercise using an empty line followed by three dashes!
   For now, there are 2 types of exercises. The 'normal' type, which is the default, 
   and the multiple choice exercise. To create a multiple choice exercise, 
   add 'type:MultipleChoiceExercise' to the '---' that starts a new exercise. 
   This file contains some examples. Additionally, a multiple choice exercise can have a graph 
   in its pre exercise code, which is then loaded along with the exercise. The last exercise of this file
   contains an example of this.
4. Consult the documentation at: https://github.com/Data-Camp/datacamp if you're stuck
  
In the assignement, you can explain statistical concepts or R functionality. Assignments are written in (R) Markdown.

You can emphasize important words by putting them in **bold** or *italics*, or indicate that some parts are `r_code` with backticks, but what's really cool is that you can incorporate LATEX style formula's, e.g. $\frac{E(R_i) - R_f}{\beta_i} = E(R_m) - R_f$ You can even add lists, to structure your explanation: 
- item one
- item two

Or you could link to interesting content: [this is a link](http://en.wikipedia.org/wiki/Markdown), or [another useful link](http://www.rstudio.com/ide/docs/authoring/using_markdown...).

*** =instructions
  - Provide one instruction to your students/employees/... on what specific problem they should solve in this exercise
  - Provide a second instruction here.
  - ect.

*** =hint

Hints help the students to find a correct solution for the exercise. Hints are optional, but their usage is highly recommended.

*** =pre_exercise_code

```{r,eval=FALSE}
# Pre-exercise code is executed before the exercise starts (what's in a name...)
# It can be used to:
# Pre-load a dataset
# Render graphs that are shown at the start of the exercise
# ...
```

*** =solution

```{r,eval=FALSE}
# The solution code solves the assignement. Make sure the solution passes the submission correctness test (we will check this;-)!
```

*** =sample_code

```{r,eval=FALSE}
# The sample code is what is shown in the students editor by default
```

*** =sct

```{r,eval=FALSE}
# The Submission Correctness Test code
# It takes as input the students workspace, his code and what was printed to the console during the exercise.
# Based on these inputs the SCT returns:
# (i) whether the students code was correct
# (ii) a message to the student to either help him find what was wrong or congragulate him on finding the solution.
DM.result = list(TRUE,"Well done!")
```

--- type:MultipleChoiceExercise
## This is a multiple choice exercise!

Assigment here.

*** =instructions

- Option 1
- Option 2
- ...
  
*** =hint

Hint here. 

*** =pre_exercise_code

```{r,eval=FALSE}
# Pre-exercise code here
```

*** =solution

```{r,eval=FALSE}
# Solution code here 
```

*** =sample_code

```{r,eval=FALSE}
# Sample code here
if (DM.result == 1) {
  DM.result = list(TRUE,"Well done!")
} else {
  DM.result = list(FALSE,"Wrong!")
}
```

*** =sct

```{r,eval=FALSE}
# Submission Correctness Test here
```

--- type:MultipleChoiceExercise contains_graph:TRUE
## This multiple choice exercise contains a graph!

Assigment here.

*** =instructions

- Option 1
- Option 2
- ...
  
*** =hint

Hint here. 

*** =pre_exercise_code

```{r,eval=FALSE}
# Draw graph here
hist(rnorm(1000))
```

*** =solution

```{r,eval=FALSE}
# Solution code here 
```

*** =sample_code

```{r,eval=FALSE}
# Sample code here
```

*** =sct

```{r,eval=FALSE}
# Submission Correctness Test here
if (DM.result == 1) {
  DM.result = list(TRUE,"Well done!")
} else {
  DM.result = list(FALSE,"Wrong!")
}
```
